\documentclass[11pt,oldfontcommands,oneside,onecolumn]{memoir}
\usepackage[utf8]{inputenc}\usepackage[T1]{fontenc}


\title{Food for thought}\author{Julian Wergieluk}\date{}
\input{../latex-common/preamble}\input{../latex-common/commands}

\setcounter{secnumdepth}{4}\renewcommand{\theparagraph}{\arabic{paragraph}.}
\renewcommand{\theenumi}{\Alph{enumi}.}
\renewcommand{\labelenumi}{\theenumi}

\usepackage{paralist}
%\setlength{\parindent}{0pt}

\newcommand{\showsolutions}



\begin{document}
\chapterstyle{bringhurst}
\frontmatter
\maketitle
\newpage\tableofcontents

\mainmatter




\chapter{Stochastic calculus}

\paragraph{Transformations of the Brownian Motion. } Let $B,W$ be independent Brownian motions.
Show that the processes
\begin{enumerate}
    \item $\left( -B_t \right)$,
    \item $\left( B_{T-t}-B_t \right)$,
    \item $\left( c B_{t/c^2} \right)$ with $c\in\R \setminus \left\{ 0 \right\}$,
    \item $X= \left( tB_{1/t} \right)$ with $X_0=0$, and
    \item $\left( cB_i + \sqrt{1-c^2}W_t \right)$ for $0<c<1$
\end{enumerate}
are also Brownian motions. Specify the relevant filtrations.


\paragraph{Maximum processes of the Brownian Motion. } 
Show that the process $W - W^*$ has independent increments. $W$ denotes
Brownian Motion and $X^*_t= \max_{0 \leq s \leq t} X_s$ is the maximum process of 
a \cadlag process $X$.


\paragraph{Transformations of matringales.} (a) If $M$ is a martingale and
$\varphi$ is a convex function such that each $\varphi(M_t)$ is integrable,
show that $\varphi(M)$ is a submartingale.  (b) If in (a) $M$ is a
submartingale, and $\varphi$ is also non-decreasing on the range of $M$, show
that again $\varphi(M)$ is a submartingale.


\paragraph{A basic submartingale transformation.}
Let $M$ be a submartingale and $\varphi$ a non-decreasing function
on the range of $M$. If $\varphi M_t$ is integrable for each $t$ then 
$\left( \varphi M_t \right)_t$ is again a submartingale.


\paragraph{Basic properties of local martingales. } A bounded local martingale is a 
true martingale. A local martingale with bounded jumps is a honest martingale.





\paragraph{Ornstein-Uhlenbeck process. } Consider a Ornstein-Uhlenbeck process
\begin{equation}
	dX_t = -\lambda \left( X_t -\theta \right)dt + \sigma dW_t, \quad X_0\in\R.
\end{equation}
Prove that
\begin{eqnarray}
	EX_t &=& \theta + e^{-\lambda t }\left( X_0 - \theta \right) \\
	\var X_t &=&  \frac{\sigma^2}{ 2 \lambda} \left( 1 - e^{-2\lambda t } \right).
\end{eqnarray}
Martin proved that using a basic properties of affine processes.



\paragraph{Feller processes. Not Feller by discontinuity at zero. }
Find a Markov process violating the continuity part of 
the Feller property, namely
\begin{equation}
\lim_{t\to 0} P_t f(x) = f(x) \quad \forall f \in C_0 \ \forall x\in \R
\end{equation}
but perhaps preserving the $C_0$ property $P_t C_0 \subset C_0$.




\paragraph{L\'evy martingales.  } Every L\'evy process which is a local
martingale is also a true martingale.












\chapter{Probability theory}

\paragraph{Independence and transformations. } Let random variables $X_1,\ldots,X_n$ and
$Y_1,\ldots,Y_k$ satisfy $X_i \upmodels Y_j$ for all $i$ and $j$.
\begin{enumerate}
    \item It follows that $g(X_i)$ and $h(Y_j)$ are independent for any $i$ and $j$.
    \item The following generalization of the above result is not true. Given
any Borel functions $f$ and $g$ of suitable dimensionality 
$f(X_1,\ldots,X_n)$ may be not independent of $g(Y_1,\ldots,Y_k)$.
\end{enumerate}

\paragraph{Solution. } $\sigma\left( g(X_i) \right) \subset \sigma(X)$ and therefore 
$A\in\sigma(g(X_i))$ and $B\in\sigma(h(Y_i))$ implies $P(A\cap B)=P(A)P(B)$.



\paragraph{Monotonic transformations of RVs. }   A monotonic transformation of a real
valued random variable with a continuous distribution function has a continuous
distribution function. 
%\url{http://math.stackexchange.com/questions/78101/monotonic-transformation-of-continuous-random-variable-are-continuous}


















\chapter{Statistics}


\section{Exponential families}

\paragraph{Non-central exponential distribution is not an exponential family. } % statistics
Show that non-central exponential distribution with the density
\begin{equation}
    p_\theta(x) = \frac{1}{\theta} \exp\left( 1- \frac{x}{\theta} \right)1_{\R_{>\theta}}(x)
\end{equation}
and $\theta\in\R$ is not an exponential family. 

\paragraph{Solution. } Assume 
\begin{equation}
    p_\theta(x)=h(x)c(\theta)\exp(w(\theta) t(x)).
\end{equation}
For any fixed $\theta$ and $x<\theta$ we have
$$p_\theta(x)=h(x)c(\theta)\exp(w(\theta) t(x))=0,$$ but on the other hand
$p_\theta(x)>0$ for all $x>\theta$. This implies $c(\theta)>0$ and $h(x)=0$ for
all $x<\theta$. Since $\theta$ was arbitrary, we get $h(x)\equiv 0$, a
contradiction.










\end{document}
