

\paragraph{Independence and transformations. } Let random variables $X_1,\ldots,X_n$ and
$Y_1,\ldots,Y_k$ satisfy $X_i \upmodels Y_j$ for all $i$ and $i$.
\begin{enumerate}
    \item It follows that $g(X_i)$ and $h(Y_j)$ are independent for any $i$ and $j$.
    \item A generalization of the above result is not true. Given
any Borel functions $f$ and $g$ of suitable dimensionality 
$f(X_1,\ldots,X_n)$ may be not independent of $g(Y_1,\ldots,Y_k)$.
\end{enumerate}


\paragraph{Monotonic transformations of RVs. }   A monotonic transformation of a real
valued random variable with continuous distribution function has continuous
distribution function. 
%\url{http://math.stackexchange.com/questions/78101/monotonic-transformation-of-continuous-random-variable-are-continuous}


\paragraph{Transformations of matringales.} (a) If $M$ is a martingale and
$\varphi$ is a convex function such that each $\varphi(M_t)$ is integrable,
show that $\varphi(M)$ is a submartingale.  (b) If in (a) $M$ is a submartingale,
and $\varphi$ is also non-decreasing on the range of $M$, show that again $\varphi(M)$ is a
submartingale.


\paragraph{Basic properties of local martingales. } A bounded local martingale is a 
true martingale. A local martingale with bounded jumps is a honest martingale.


\paragraph{Levy martingales.  } Every Levy process which is a local martingale is also a true martingale.


\paragraph{Maximum processes of the Brownian Motion. } 
Show that the process $W - W^*$ has independent increments. $W$ denotes
Brownian Motion and $X^*_t= \max_{0 \leq s \leq t} X_s$ is the maximum process of 
a \cadlag process $X$.



\paragraph{Independence. }
Let $(\Omega, \mathcal A, P)$ be a probablity space and let $\mathcal F$ and
$\mathcal G$ be two independent sub-$\sigma$-algebras of $\mathcal A$.

\begin{enumerate} 
\item If $X: \Omega \to (\R, \mathcal B)$ is a
    real-valued random variable and $X$ is both $\mathcal F$-measurable
    and $\mathcal G$-measurable then $X$ is a.s.~constant.
\end{enumerate}


\paragraph{Gamma distribution. Basic facts. }

Characterised by the density, non-zero for positive $x$:
\begin{equation}
p_{\alpha, \beta}(x) = \frac{\beta^\alpha}{ \Gamma(\alpha)} x^{\alpha-1}e^{-\beta x}
\end{equation}

\begin{enumerate}
\item Let $X$ and $Y$ be non-degenerate and independent. 
    $X+Y$ and $\frac{X}{X+Y}$ are independent iff $X$ and $Y$
    are both Gamma distributed with the same scale parameter. 
    \src Lukacs 1953.
\end{enumerate}





\paragraph{A basic submartinale transformation}
Let $M$ be a submartingale and $\varphi$ a non-decreasing function
on the range of $M$. If $\varphi M_t$ is integrable for each $t$ then 
$\left( \varphi M_t \right)_t$ is again a submartingale.




\paragraph{Flow of information}
For a given $X$ decribe the class of random varibles with properies
\begin{enumerate}
\item $E X|Y = X$,
\item $\textrm Var X|Y = X$, and
\item $\textrm Var Y|X = \textrm Var Y$.
\end{enumerate}

Do you need any assumptions? What is the context of this problem again?  




\paragraph{Not Feller by discontinuity at zero}
Find a Markov process viotating the continuity part of 
the Feller property, namely
\begin{equation}
\lim_{t\to 0} P_t f(x) = f(x) \quad \forall f \in C_0 \ \forall x\in \R
\end{equation}
but perhaps preserving the $C_0$ property $P_t C_0 \subset C_0$.







\paragraph{Convergence of a compounded Poisson process}
What is the convergence behavior for $k\to \infty$ of the process 
\begin{equation}
X = \left(  \frac{1}{k} N_t^k - t  \right)_t
\end{equation}
where $N^k$ is a Poisson process with intensity $k$. 

\begin{enumerate}
\item Is it clear that $E\left( X_t \right) \to t$ and $\textrm{Var} \left( X_t \right)\to 0$.
\item Do we also have ucp convergence?
\end{enumerate}









\paragraph{Quasi-left-continuity}
A process $X$ is said to be quasi-left-continuous if for every stopping
time $\tau$ and a seqence of stopping times $\tau_n$ increasing to $\tau$
\begin{equation}
X_{\tau_n} \to X_{\tau}
\label{}
\end{equation}
holds almost surely.
\begin{enumerate}
\item This means the jumps of $X$ can not be predicted.
\item Every Poisson process is quasi-left-continuous.
\end{enumerate}





